get number of farms

### 2021-03-15 workflow/predict_farm_numbers.Rmd
adding farm numbers, quality control fixes, as well as continent group information

```{r}
library(tidyverse)
library(tidymodels)
library(WDI)
library(countrycode)

raw <- read_csv("marine/data/n_farms_production_data.csv")

ready <- raw %>% 
  mutate(iso2c = purrr::map_chr(.x = iso3c, 
                           ~countrycode(sourcevar = .x, 
                                        origin = "iso3c", 
                                        destination = "iso2c")))

>>>>

```{r}
library(tidyverse)
library(janitor)
library(tidymodels)
library(WDI)
library(countrycode)

aq_info <- read_csv('/home/shares/clean-seafood/raw_data/FAO/production/CL_FI_COUNTRY_GROUPS.csv') %>% 
  clean_names() %>% 
  select(iso3_code, geo_region_group, continent_group, eco_class_group)

raw <- read_csv("/home/blasco/github/aquaculture_mapping/marine/data/n_farms_production_data.csv") %>% 
  left_join(aq_info, by = c('iso3c' = 'iso3_code'))

aq_types <- raw %>% 
  filter(!is.na(n_farms)) %>% 
  mutate(tonnes_per_farm = fao_tonnes_production/n_farms) %>% 
  group_by(continent_group, group) %>% 
  summarise(tonnes_per_farm = mean(tonnes_per_farm))
```

```{r}
ready <- raw %>% 
  mutate(iso2c = purrr::map_chr(.x = iso3c, 
                           ~countrycode(sourcevar = .x, 
                                        origin = "iso3c", 
                                        destination = "iso2c")))
